Unsupervised embeddings capture latent structure of scientific mobility

### 2020-02-24 paper/current/main.tex
minor_equation_label_edit

\js{I think we need a results, geographical distance with exponential function, emb distance with power-law function. And It will goes to supplement for sure}
We consider separate variants of $f(r_{ij})$ for geographic distance, $g_{ij}$, and the embedding distance, $d_{ij}$, report the best-fit model of each distance.
For geographic distance, we use the power-law function of the gravity law, with $f(g_{ij})= g^{-\alpha}_{ij}$, where $\alpha$ is estimated from the data. 
For embedding distance , we use the exponential function, with $f(d_{ij}) = e^{-\beta d_{ij}}$, where $\beta$ is estimated from the data. 
To estimate parameters $\alpha$ and $\beta$ are estimated by log-transforming each variant of \label{eq:gravity_flux}, obtaining Eq.~\ref{eq:linear_flux_geo} and Eq.~\ref{eq:linear_flux_emb} in the form of linear equations, and fitting parameters using linear regression.

@@

\begin{equation}
    \label{eq:gravity_relationship}
      p(j|i) \propto {\mu_j}* \exp(\cos(v_i,v_j))
\end{equation}

@@

\begin{equation}
    \label{eq:gravity_relationship}
    \sum_{j\in\mathpzc{N}_i} p(j|i) = 1
\end{equation}

@@

\begin{equation}
    \label{eq:gravity_relationship}
    p(j|i) \propto \frac{{\mu_j}* \exp(\cos(v_i,v_j)}{\sum_{k\in\mathpzc{N}_i} {\mu_k}* \exp(\cos(v_i,v_k))}
\end{equation}

>>>>

\js{I think we need a results, geographical distance with exponential function, emb distance with power-law function. And It will goes to supplement for sure}
We consider separate variants of $f(r_{ij})$ for geographic distance, $g_{ij}$, and the embedding distance, $d_{ij}$, report the best-fit model of each distance.
For geographic distance, we use the power-law function of the gravity law, with $f(g_{ij})= g^{-\alpha}_{ij}$, where $\alpha$ is estimated from the data. 
For embedding distance , we use the exponential function, with $f(d_{ij}) = e^{-\beta d_{ij}}$, where $\beta$ is estimated from the data. 
To estimate parameters $\alpha$ and $\beta$ are estimated by log-transforming each variant of \ref{eq:gravity_flux}, obtaining Eq.~\ref{eq:linear_flux_geo} and Eq.~\ref{eq:linear_flux_emb} in the form of linear equations, and fitting parameters using linear regression.

@@

\begin{equation}
    \label{eq:conditional probability}
      p(j|i) \propto {\mu_j}* \exp(\cos(v_i,v_j))
\end{equation}

@@

\begin{equation}
    \label{eq:sum of the conditional probabiitliy}
    \sum_{j\in\mathpzc{N}_i} p(j|i) = 1
\end{equation}

@@

\begin{equation}
    p(j|i) \propto \frac{{\mu_j}* \exp(\cos(v_i,v_j)}{\sum_{k\in\mathpzc{N}_i} {\mu_k}* \exp(\cos(v_i,v_k))}
\end{equation}
